---
title: "omicron sentiment analysis1"
output: word_document
---

``
```
```{r}
#List Of Packages Used
library(RColorBrewer) 
library(tm)
library(twitteR)
library(ROAuth)
library(plyr)
library(stringr)
library(base64enc)
library(SnowballC)
library(ggplot2)
library(maps)
```

## R Markdown
```{r}
consumer_key = 'LS8TNNyEFgSJS9dsGgIjzRtBp'
consumer_secret = 'OCc77g0cYjZaaZ3BPkufbxwqbcbThFTKDyvJ3y2BCzpkFHTgWT' 
access_token= '1479689862504583173-1RW8rAkio3oCNeXX7OHjaYhA6nfSD5' 
access_secret = 'htLppM4lfGgoZkJ80rzo6Hlz3FwA9waHh9nPk3D7DfRpl'
```

```{r}
requestURL<- "https://api.twitter.com/oauth/request_token"
accessURL<- "https://api.twitter.com/oauth/access_token"
authURL<- "https://api.twitter.com/oauth/authorize"
```


```{r}
setup_twitter_oauth(consumer_key ,consumer_secret,access_token,access_secret)
```


```{r}
#search TWitter
users<- searchTwitteR("#omicron", resultType="recent",n=300, lang="en")
 
tweet.df = do.call("rbind",lapply(users,as.data.frame))
```



```{r}
#Plotting data on map
map('world')
points(tweet.df$longitude,tweet.df$latitude, pch=20, cex=1, col="red")
```

```{r}
#Viewing the data
View(tweet.df)
```

```{r}
#Reading sentiment analysis data from Txt document
pos.words = scan('./positive-words.txt', what='character', comment.char=';')
neg.words = scan('./negative-words.txt', what='character', comment.char=';')
```

```{r}
#Appending some more words to actual words
pos.words = c(pos.words, 'new','nice' ,'good', 'horizon')
neg.words = c(neg.words, 'wtf', 'behind','feels', 'ugly', 'back','worse' , 'shitty', 'bad', 'no','freaking','sucks','horrible')
```

```{r}
#converting Into dataFrame
test <-ldply(users,function(t)t$toDataFrame())
test
```

```{r}
score.sentiment = function(sentences, pos.words, neg.words, .progress='none')
{
  require(plyr)
  require(stringr)
  scores = laply(sentences, function(sentence, pos.words, neg.words) {
    sentence = gsub('[[:punct:]]', '', sentence)
    sentence = gsub('[[:cntrl:]]', '', sentence)
    sentence = gsub('\\d+', '', sentence)
    sentence = tolower(sentence)
    word.list = str_split(sentence, '\\s+')
    words = unlist(word.list)
    pos.matches = match(words, pos.words)
    neg.matches = match(words, neg.words)
    pos.matches = !is.na(pos.matches)
    neg.matches = !is.na(neg.matches)
    score <- sum(pos.matches) - sum(neg.matches)
    return(score)
  }, pos.words, neg.words, .progress=.progress )
  
  scores.df = data.frame(score=scores, text=sentences)
  return(scores.df)
}
```

```{r}
result <- score.sentiment(test$text,pos.words,neg.words)
result
#summarlizing data
summary(result$score)
```

```{r}
#Histogram
hist(result$score,col="yellow", main="Score of tweets",ylab=" Count of tweets")
```

```{r}
#Count No of Tweets
count(result$score)
```

```{r}
#ploting the tweets on qplot
qplot(result$score,xlab = "Score of tweets")
```

```{r}

require(wordcloud)

```

```{r}
negativeTweets = subset(result, score < 0)$text

```

```{r}
corpus = Corpus(VectorSource(negativeTweets))
# corpus = Corpus(VectorSource(cmail))
# create term-document matrix
tdm = TermDocumentMatrix(
  corpus,
  control = list(
    wordLengths=c(3,20),
    removePunctuation = TRUE,
    stopwords = c("the", "a", stopwords("english")),
    removeNumbers = TRUE, tolower = TRUE) )

```

```{r}
# convert as matrix
tdm = as.matrix(tdm)

```

```{r}
# get word counts in decreasing order
word_freqs = sort(rowSums(tdm), decreasing=TRUE) 
word_freqs = word_freqs[-(1:12)]
# create a data frame with words and their frequencies
dm = data.frame(word=names(word_freqs), freq=word_freqs)

```

```{r}
#Plot corpus in a clored graph; need RColorBrewer package

wordcloud(head(dm$word, 100), head(dm$freq, 100), random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```


```{r}
positiveTweets = subset(result, score > 0)$text
```

```{r}
corpus = Corpus(VectorSource(positiveTweets))
# corpus = Corpus(VectorSource(cmail))
# create term-document matrix
tdm = TermDocumentMatrix(
  corpus,
  control = list(
    wordLengths=c(3,20),
    removePunctuation = TRUE,
    stopwords = c("the", "a", stopwords("english")),
    removeNumbers = TRUE, tolower = TRUE) )
```


```{r}
# convert as matrix
tdm = as.matrix(tdm)
```

```{r}
# get word counts in decreasing order
word_freqs = sort(rowSums(tdm), decreasing=TRUE) 
word_freqs = word_freqs[-(1:12)]
# create a data frame with words and their frequencies
dm = data.frame(word=names(word_freqs), freq=word_freqs)
```

```{r}
wordcloud(head(dm$word, 100), head(dm$freq, 100), random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

```{r}
NeutralTweets = subset(result, score = 0)$text
```

```{r}
corpus = Corpus(VectorSource(NeutralTweets))
# corpus = Corpus(VectorSource(cmail))
# create term-document matrix
tdm = TermDocumentMatrix(
  corpus,
  control = list(
    wordLengths=c(3,20),
    removePunctuation = TRUE,
    stopwords = c("the", "a", stopwords("english")),
    removeNumbers = TRUE, tolower = TRUE) )
```


```{r}
# convert as matrix
tdm = as.matrix(tdm)
```

```{r}
# get word counts in decreasing order
word_freqs = sort(rowSums(tdm), decreasing=TRUE) 
word_freqs = word_freqs[-(1:12)]
# create a data frame with words and their frequencies
dm = data.frame(word=names(word_freqs), freq=word_freqs)
```

```{r}
wordcloud(head(dm$word, 100), head(dm$freq, 100), random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

